---
title: "Report"
author: "Jingyi Niu"
date: "October 19, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```


## Data Manipulation

The raw data contains three different products: STRAWBERRY, RASPBERRY, STRAWBERRY. Our interest is focus on the RASPBERRY data. Therefore, the `filter` function in `dplyr` package is been used to extract all data about RASPBERRY.

The main difficult in data manipulation is that some key information are combined togather in a single variable, for example: **Data Item** contains the type information, and the type information contains three key informations (ACRES HARVESTED, PRODUCTION, YIELD).

To extrac these informations, the `separate` function in package `tidyr` is been used for many times.

Furthermore, the variable `Value` in this dataset is not stored in numeric for two reasons:
1. the value is in the format of `123,456,789`, the comma needs to be remove.
2. there exists `(D)` values.

To do our data analysis, the variable `Value` need to be converted into numeric. The `str_replace_all` function in the `stringr` package is been used to do this conversion.


Now the data is been manipulated into a tidy format, like this:

```{r echo=F}
library(tidyverse)
library(magrittr)
load("./04_rasp.Rdata")
```

```{r echo=F}
head(dat2, 5) %>% knitr::kable() 
```


It can be noticed that there exists many NA in the variable `YIELD` and `ACRES HARVESTED`. 

## The analysis of Harvested Areas

In this part, we focus on the Harvested Areas(in Acres).

The Harvested Areas of states in 2015 are listed below:

```{r echo = F}
# ACRES_HARVESTED in Acre in 2015
dat2 %>% 
  filter(Year == 2015) %>%
  group_by(State) %>%
  arrange(desc(ACRES_HARVESTED)) %>%
  select(-PRODUCTION, -YIELD) %>% knitr::kable()
```

```{r echo = F}
# plot
dat2 %>% 
  filter(Year == 2015) %>%
  ggplot(aes(x = State, y = ACRES_HARVESTED)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Area of Harvested in 2015")
```


The states which has the top 2 Harvested Areas are listed below:

```{r echo = F}
# ACRES_HARVESTED in Acre top 2
dat2 %>% 
  group_by(Year) %>%
  # arrange(desc(ACRES_HARVESTED)) %>%
  top_n(2, ACRES_HARVESTED) %>%
  select(-PRODUCTION, -YIELD) %>% knitr::kable()
```

The Harvested Areas of the last 5 years:

```{r echo = F}
# plot
dat2 %>% 
  ggplot(aes(x = Year, y = ACRES_HARVESTED, color = State)) +
  geom_line() +
  labs(title = "Area of Harvested of the last 5 years")
```

From the above table and graph, it can be seen that :

1. The Area of Harvested of 2 States(CALIFORNIA, WASHINGTON) are much higher than OREGON
2. Data missing for year 2018 and 2019.
3. The Area of Harvested of California was decreasing.


## The analysis of PRODUCTION

In this part, we focus on the PRODUCTION(in lbs).

The PRODUCTION of states in 2015 are listed below:

```{r echo = F}
# PRODUCTION (in lbs) in 2015
dat2 %>% 
  filter(Year == 2015) %>%
  group_by(State) %>%
  arrange(desc(PRODUCTION)) %>%
  select(-YIELD, -ACRES_HARVESTED) %>% knitr::kable()

# plot
dat2 %>% 
  filter(Year == 2015) %>%
  ggplot(aes(x = State, y = PRODUCTION)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "PRODUCTION (in lbs) in 2015")
```


The states which has the top 2 PRODUCTION are listed below:

```{r}
# PRODUCTION (in lbs)  top 3
dat2 %>% 
  group_by(Year) %>%
  top_n(2, PRODUCTION) %>%
  select(-YIELD, -ACRES_HARVESTED) %>% knitr::kable()
```

The PRODUCTION of the last 5 years:

```{r}
dat2 %>% 
  ggplot(aes(x = Year, y = PRODUCTION, color = State)) +
  geom_line() +
  labs(title = "PRODUCTION (in lbs) of the last 5 years")

```

From the above table and graph, it can be seen that :

1. The Production of 2 States(CALIFORNIA, WASHINGTON) are much higher than OREGON
2. Data missing for Oregon after year 2017.
3. The Production of 2 States are keep decreasing for the last 5 years.



## The analysis of YIELD

In this part, we focus on the YIELD(in lbs per Acre).

The YIELD of states in 2015 are listed below:

```{r echo = F}
# YIELD in  lbs per Acre  in 2015
dat2 %>% 
  filter(Year == 2015) %>%
  group_by(State) %>%
  arrange(desc(YIELD)) %>%
  select(-PRODUCTION, -ACRES_HARVESTED) %>% knitr::kable()

# plot
dat2 %>% 
  filter(Year == 2015) %>%
  ggplot(aes(x = State, y = YIELD)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "YIELD (in lbs per Acre) in 2015")
```

The states which has the top 3 YIELD are listed below:

```{r echo = F}
# YIELD (in lbs per Acre) top 3
dat2 %>% 
  group_by(Year) %>%
  top_n(2, YIELD) %>%
  select(-PRODUCTION, -ACRES_HARVESTED) %>% knitr::kable()
```

The YIELD of the last 5 years:

```{r}
# plot
dat2 %>% 
  ggplot(aes(x = Year, y = YIELD, color = State)) +
  geom_line() +
  labs(title = "YIELD (in lbs per Acre) of the last 5 years")
```

From the above table and graph, it can be seen that :

1. The YIELD of Clifornia was decreasing from 2016 to 2017.
2. Data missing for year 2018 and 2019.
3. The YIELD of Clifornia is much higher than the rest.

**It is very interesting that 3 States (CALIFORNIA, OREGON, WASHINGTON) has much higher YIELD(in lbs per Acre) than the other states. Further study may be needed.**



## YIELD on the US Map

In this part, we plot the YIELD of 3 States on the map of United States.

```{r echo = F}
library(usmap)

dat2 %>%
  filter(Year == 2015) %>%
  select(State, YIELD) %>%
  mutate(State = str_to_title(State)) %>%
  right_join(statepop, by = c("State" = "full")) -> dat3
  
plot_usmap(data = dat3, regions = "states", values = "YIELD", color = "white") + 
  scale_fill_continuous(name = "YIELD", low = "yellow", high = "red") +
  theme(legend.position = "right")
```

It can be seen that the State that have much higher YIELD is located in the middle of **West Coast**. The weather may be a great reason of the high YIELD.











